### 2022-05-13 supplement.Rmd

Meta-analytic methods require an estimate of the sampling variance of each included experiment [@harrer2021]. For within-participant experimental designs (i.e., repeated measures on the same individuals in different conditions), this sampling variance needs to reflect that repeated measures from the same participant will be more similar to one another than measures from two randomly selected participants, thus not providing independent information. This is reflected by the correlation term $r$ in the formula of the standard error of the effect size ${SE}_\text{rotation}$ (see Methods) [@goulet-pelletier2018]. This correlation between repeated measures unfortunately tends to go unreported in research articles. In fact, none of the `r descs$n_articles` articles in the present meta-analysis provided a direct numerical estimate for the correlation between infants' looking times in the novel and familiar rotation object conditions.

@@

3. Compute the standard deviation of the mean looking time difference: $${SD}_\text{diff}=\frac{m_\text{diff}}{d_\text{diff}}$$

4. Extract the standard deviations ${SD}_\text{novel}$ and ${SD}_\text{familiar}$ of looking times within each of the two conditions.

5. Compute the observed correlation between conditions based on rearranging an equation by @cohen1988: $$r=\frac{{SD}_\text{diff}^2-{SD}_\text{novel}^2-{SD}_\text{familiar}}{-2\cdot{SD}_\text{novel}^2\cdot{SD}_\text{familiar}^2}$$

Across these $`r nrow(dat_ri_empirical)`$ experiments, the average observed correlation was $r = `r summ_ri_empirical["Mean"]`$ (median $r = `r summ_ri_empirical["Median"]`$, range [`r summ_ri_empirical["Min."]`, `r summ_ri_empirical["Max."]`]). However, we decided to assume a correlation of $r  = .50$ when computing ${SE}_\text{rotation}$ for all `r descs$n_experiments` experiments. This was to ensure the comparability of our methods to meta-analyses of between-participant studies [@cohen1988; @lakens2013; @morris2002]. We ran a sensitivity analysis to test the robustness of our Bayesian meta-analytic model against this assumption (Supplementary Table 4).

@@

We used a simplified two-level version (i.e., dropping the article level) of our frequentist three-level model to further correct our results for publication bias. We conducted a trim-and-fill analysis [@duval2000] to impute possible effect sizes of non-published experiments and then observed their influence on the meta-analytic effect size (Supplementary Tables 8 and 9).

Next, we used selection models to approximate the selection process of experiments into the meta-analysis under the assumption that experiments that observe significant effects (i.e., with low p-values) are more likely to get published. We ran one selection model assuming a weight function with fixed *p*-value cutoffs [@vevea1995] at *p* = .01, *p* = .05, and *p* = .30, as well as multiple models with a priori selection functions that assume bias of varying severity [@vevea2005]. These analyses show that our results are robust to small to medium amounts of publication bias (Supplementary Tables 8 and 9).

@@

(ref:figs1-caption) **Meta-analysis of gender differences.** A Bayesian three-level meta-analysis provided evidence for a small gender difference in mental rotation performance between male and female infants. White squares indicate the effect sizes (Hedges' $g$) for gender difference in all individual experiments and black lines their 95% confidence intervals. Note that for experiments that observed a non-significant gender difference and did not specify the exact size of this effect, we assumed an effect size of $g = 0.00$. Gray bars indicate the 95% and 50% Bayesian credible interval (CrI) based on a Bayesian three-level random-effects model. Note that these intervals got shrunk towards the meta-analytic effect size because of partial pooling, that is, the three-level model regularizing the impact of experiments with small sample sizes and/or unrealistically large effect sizes. The last line shows the meta-analytic effect size from the three-level model (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).

>>>>

Meta-analytic methods require an estimate of the sampling variance of each included experiment [@harrer2021]. For within-participant experimental designs, this sampling variance needs to account for the fact that repeated measures are taken from the same individuals in different conditions. Repeated measures from the same participant will be more similar to one another than measures from two randomly selected participants and thus do not provide independent information. This is accounted for by the correlation term $r$ in the formula of the standard error of the effect size ${SE}_\text{rotation}$ (see Methods) [@goulet-pelletier2018]. However, the correlation between repeated measures tends to go unreported in research articles. In fact, none of the `r descs$n_articles` articles in the present meta-analysis provided a direct numerical estimate for the correlation between infants' looking times in the novel and familiar rotation object conditions.

@@

3. Compute the standard deviation ($SD$) of the mean looking time difference: $${SD}_\text{diff}=\frac{m_\text{diff}}{d_\text{diff}}$$

4. Extract the standard deviation of looking times for the novel condition ${SD}_\text{novel}$ and the familiar condition ${SD}_\text{familiar}$.

5. Compute the observed correlation between conditions based on a rearranged equation by @cohen1988: $$r=\frac{{SD}_\text{diff}^2-{SD}_\text{novel}^2-{SD}_\text{familiar}}{-2\cdot{SD}_\text{novel}^2\cdot{SD}_\text{familiar}^2}$$

Across these $`r nrow(dat_ri_empirical)`$ experiments, the average observed correlation was $r = `r summ_ri_empirical["Mean"]`$ (median $r = `r summ_ri_empirical["Median"]`$, range [`r summ_ri_empirical["Min."]`, `r summ_ri_empirical["Max."]`]). However, we decided to assume a correlation of $r  = .50$ when computing the effect size ${SE}_\text{rotation}$ for all `r descs$n_experiments` experiments. This was to ensure the comparability of our methods to meta-analyses of between-participant studies [@cohen1988; @lakens2013; @morris2002]. To  evaluate the robustness of our Bayesian meta-analytic model against the assumption of a correlation of $r  = .50$ we ran a sensitivity analysis (Supplementary Table 4).

@@

We used trim-and-fill analysis and selection models to examine if and how our meta-analytic results would change under different degrees of publication bias. For both of these types of models, we used a simplified two-level version of our frequentist three-level model as a basis. In our first step, we computed a trim-and-fill model [@duval2000] by imputing possible effect sizes of non-published experiments. This new model produces a symmetric funnel plot with no association between effect sizes and standard errors (Supplementary Tables 8 and 9).

In our next step, we used selection models to approximate the process by which experiments got selected into the meta-analysis. These models were based on the assumption that experiments yielding significant effects (i.e., small *p*-values) are more likely to get published. Specifically, we ran one selection model assuming a weight function with fixed *p*-value cutoffs [@vevea1995] at *p* = .01, *p* = .05, and *p* = .30. Additionally, we ran multiple models with a priori selection functions assuming biases of varying severity [@vevea2005]. These analyses  revealed that our results are robust to small to medium publication bias (Supplementary Tables 8 and 9).

@@

(ref:figs1-caption) **Meta-analysis of gender differences.** A Bayesian three-level meta-analysis provided evidence for a small gender difference in mental rotation performance between male and female infants. White squares indicate the effect sizes (Hedges' $g$) of gender differences in all individual experiments and black lines indicate their 95% confidence intervals. For experiments resulting in a non-significant gender difference and for which the authors did not specify the exact size of this effect, we assumed an effect size of $g = 0.00$. Gray bars depict the 95% and 50% Bayesian credible interval (CrI) based on a Bayesian three-level random-effects model. These intervals got shrunk towards the meta-analytic effect size because of partial pooling, that is, the three-level model regularizing the impact of experiments with small sample sizes and/or unrealistically large effect sizes. The bold line at the bottom of the figure shows the meta-analytic effect size obtained from the three-level model (black dot) together with its 95% CrI (black line) and its posterior distribution (gray curve).
